|

### 2021-02-24 manuscript/article.Rmd
fix typos

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the cleaning of containers and the use of insecticide to reduce
vector breeding, especially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site elimination and insecticide
spraying are labour-intensive processes, which are often carried out
inconsistently by developing states [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving their health agency's performance in
mosquito control is essential to the effectiveness of anti-*Aedes* programmes.

@@

```{r, echo = FALSE, results='asis', warning=FALSE, cache=T}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[3]], mprod[[4]],
          mprod[[1]], mprod[[2]],
          se = starprep(mprod[[3]], mprod[[4]],
                        mprod[[1]], mprod[[2]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}',
                             '\\shortstack{Houses \\\\ Visited}',
                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}'),
          keep.stat = c('ser', 'n'),
          notes = c('Robust standard errors in parenthesis.'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          label = 'tab:productivity')
```

>>>>

Mosquito control is the primary strategy to prevent *Aedes*-borne infections
[@beatty2010best; @eisen2009proactive]. The World Health Organization
recommends the cleaning of containers and the use of insecticide to reduce
vector breeding, especially in settings where human-vector contacts are
frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@world2020denguecontrol]. However, breeding site elimination and insecticide
spraying are labour-intensive processes, which are often carried out
inconsistently by developing states [@paz2015dengue; @siddiqui2016use;
@WHO2012global]. In this regard, improving the performance of their healthcare
agencies is essential to the effectiveness of anti-*Aedes* programmes.

@@

```{r, echo = FALSE, results='asis', warning=FALSE, cache=T}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[3]], mprod[[4]],
          mprod[[1]], mprod[[2]],
          se = starprep(mprod[[3]], mprod[[4]],
                        mprod[[1]], mprod[[2]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Exterminated}',
                             '\\shortstack{Larvae \\\\ Exterminated}',
                             '\\shortstack{Houses \\\\ Visited}',
                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}'),
          keep.stat = c('ser', 'n'),
          notes = c('Robust standard errors in parenthesis.'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE,
          label = 'tab:productivity')
```
